Dominance Regions for Rank Two Cluster Algebras

### 2022-04-06 dominance_regions.tex
Section 4 edits, cluster monomial proof is finished

  Here we explicitly compute the dominance regions $\cP(\lambda)$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_1}x_{k+1}^{a_2}$.
    Then $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ is precisely $\{\lambda\}$. 
    \sayDR{Check this, I am definitely convinced it works when $k$ is odd.}
  \end{proof}

>>>>

  Here we explicitly compute the dominance regions $\cP(\lambda)$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{a_1}x_{k+1}^{a_2}$.
    Then $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ is precisely $\{\lambda\}$. 
    \sayDR{Check this, I am definitely convinced it works when $k$ is odd.}
  \end{proof}
  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
  \begin{itemize}
    \item if $\lambda_1 \le 0$ and $\lambda_2 \ge 0$, the second and fourth inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_1 > 0$ and $\lambda_2 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_1$, the first and second inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_2 < 0$ and $\lambda_1 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_2$, the third and fourth inequalities become equations for lines which intersect at $\lambda$.
  \end{itemize}
  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.
